Bird species composition in coastal urban habitats

### 2020-11-12 Ms_HabitatAves.Rmd
mapa ocupancia en ggplot para primavera tambien

```{r OccuPrim, fig.width=8, fig.height=7}
Leucophaeus <-read_rds("PredPrim_Leucophaeus_pipixcan.rds")
Larus <-read_rds("PredPrim_Larus_dominicanus.rds")
Columba <-read_rds("PredPrim_Columba_livia.rds")
Larosterna <-read_rds("PredPrim_Larosterna_inca.rds")
Phalacrocorax <-read_rds("PredPrim_Phalacrocorax_bougainvillii.rds")
Pelecanus <-read_rds("PredPrim_Pelecanus_thagus.rds")

Especies <- stack(Leucophaeus, Larus, Columba, Larosterna, Phalacrocorax,  Pelecanus)
names(Especies) <- c("Columba livia", "Larosterna inca", "Larus dominicanus", "Leucophaeus pipixcan", "Pelecanus thagus", "Phalacrocorax bougainvillii")

Mytheme <- YlOrRdTheme()
Mytheme$panel.background$col <- "black"

levelplot(Especies, par.settings=Mytheme)

>>>>

```{r OccuPrim, fig.width=8, fig.height=7}
Columba <-read_rds("PredPrim_Columba_livia.rds")
Larosterna <-read_rds("PredPrim_Larosterna_inca.rds")
Larus <-read_rds("PredPrim_Larus_dominicanus.rds")
Leucophaeus <-read_rds("PredPrim_Leucophaeus_pipixcan.rds")
Phalacrocorax <-read_rds("PredPrim_Phalacrocorax_bougainvillii.rds")
Pelecanus <-read_rds("PredPrim_Pelecanus_thagus.rds")

Nombres <- c("Columba", "Larosterna", "Larus","Leucophaeus", "Phalacrocorax", "Pelecanus")
Species <- list(Columba, Larosterna, Larus, Leucophaeus, Phalacrocorax, Pelecanus)

Species_DF <- temp %>% reduce(full_join) %>% dplyr::relocate(Columba, .after = y) %>% pivot_longer(Columba:Pelecanus, names_to = "Species", values_to = "Occupancy")
